Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex
removing histograms
Pass on Introduction

%\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
%  (more coherent/compelling) as to justify the selection of these two
%  techniques?}
%\Breno{Changed the paragraph a bit to include the reuse argument.}
We selected these two techniques because they can take advantage
of existing test suites and reuse them --- in a semi-automated way
as we propose here --- to enhance the coverage of the engine under testing.
%These techniques demand different effort from developers.
Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. Test transplantation is fully automated, but it can only reveal
bugs that the original tests could reveal. This study measures the
ability of these techniques in finding bugs and the human cost
associated with each technique.

@@

To provide a brief overview of the test suites and understand if the engines
have specific testing purposes, we investigated the most common
objects and functions that each one of the JS engines employ.
To achieve this goal, we started by filtering out many non-relevant source
code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
special characters (such as parentheses, mathematical symbols, and semicolons).
For the remaining source code constructs, we search for the ``.'' character, which
indicates a function call. We then stored the function and the object that host
that function.  By manually analyzing this data, we noted many general purpose
functions, that do not provide any hint on the kind of behavior the engine is
more likely to test (such as \texttt{console.log}). We also removed these
general purpose functions. The remaining object/functions are shown at
Figure~\ref{fig:histograms}.

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \textbf{\chakra}.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \textbf{\chakra} development team as a
bug, but they did \emph{not} accept.

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case originally from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represent octal
numeric literals. This is an issue that explores a deprecated octal
token after ASI (Automatic Semicolon Insertion). The other engines
throw a SyntaxError due to the missing of the octal token, but \smonkey
returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa.
The original test case contains a string concatenation.
This is a case of validation of RegEx flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as explained by one of their developers.

>>>>

%\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
%  (more coherent/compelling) as to justify the selection of these two
%  techniques?}
%\Breno{Changed the paragraph a bit to include the reuse argument.}
We selected these two techniques because they can take advantage
of existing test suites and reuse them --- in a semi-automated way
as we propose here --- to enhance the coverage of the engine under testing.
%These techniques are semi-automated and they can demand different effort from developers.
Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. 
Test transplantation is also semi-automated
and developer intervention may be required to ensure that a test case from one engine can be performed on another engine without adaptations; 
or to verify that alarms are manifestations of real bugs and not the result of an unsupported feature or an obsolete specification.
%Test transplantation is fully automated, but it can only reveal
%bugs that the original tests could reveal. 
This study measures the ability of these techniques 
in finding bugs and the human cost associated with each technique.

@@

To provide a brief overview of the test suites and understand if the engines
have specific testing purposes, we investigated the most common
objects and functions that each one of the JS engines employ.
To achieve this goal, we started by filtering out many non-relevant source
code statements available on the test suites. We started by removing JS language constructs (such as \texttt{if}, \texttt{for}, and \texttt{var}). We then removed
special characters (such as parentheses, mathematical symbols, and semicolons).
For the remaining source code constructs, we search for the ``.'' character, which
indicates a function call. We then stored the function and the object that host
that function.  By manually analyzing this data, we noted many general purpose
functions, that do not provide any hint on the kind of behavior the engine is
more likely to test (such as \texttt{console.log}). We also removed these
general purpose functions. The remaining object/functions are shown at
Figure~\ref{fig:histograms}.

@@

\sloppy

%-----Issue \#19, Table~\ref{tab:test-transplantation-bugs}
\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.

%-----Issue \#35, Table~\ref{tab:test-transplantation-bugs}
\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case originally from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represent octal
numeric literals. This is an issue that explores a deprecated octal
token after ASI (Automatic Semicolon Insertion). The other engines
throw a SyntaxError due to the missing of the octal token, but \smonkey
returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.

%-----Issue \#2, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \textbf{\chakra} development team as a
bug, but they did \emph{not} accept.

%-----Issue \#4, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \textbf{\chakra}.

@@

%-----Issue \#18, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

%-----Issue \#24, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa.
The original test case contains a string concatenation.
This is a case of validation of RegEx flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as explained by one of their developers.
